%-------------------------
% Resume in Latex
% Author : Owen Enestvedt
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\owen}[5]{ % Adding a fifth argument for additional text
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt} % Adjust as needed
    \vspace{-3pt} % Vertical space before the additional text
    \begin{flushleft}
      \textbf{\small#5} % Additional text
    \end{flushleft}\vspace{-12pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Owen Enestvedt} \\ \vspace{1pt}
    \small 401-533-1816 $|$ \href{mailto:owen@enestvedt.net}{\underline{owen@enestvedt.net}} $|$ 
    \href{https://www.linkedin.com/in/owen-enestvedt/}{\underline{LinkedIn}} $|$
    \href{https://www.github.com/enestvedto}{\underline{GitHub}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \owen
      {Merrimack College}{North Andover, MA}
      {Bachelor of Science in Computer Science, Minor in Data Science}{August 2020 -- May 2024}{Cumulative GPA: 4.0}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Software Engineer 1}{July 2024 -- Present}
      {Dell Technologies}{}
      \resumeItemListStart
        \resumeItem{Created 5 production Jenkins pipelines to automate OCP cluster builds, CSM driver/module installations, and run sanity/integration/compliance/E2E test suites, providing daily reports with artifacts to developers via Slack and Outlook.}
        \resumeItem{Architected and implemented an automated Greenfield strategy for zero-touch detection and deployment of new OCP versions, enabling parallel deployments across multiple clusters.}
        \resumeItem{Shifted testing left by automating extensive test execution on OCP RC builds, identifying product regressions early, filing defects, and significantly reducing manual testing time and cost of technical debt.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{May 2023 -- August 2023}
      {Dell Technologies}{}
      \resumeItemListStart
        \resumeItem{Developed scripts to scan GitHub repositories and automatically update base images, create new branches, and open pull requests when outdated Dockerfile base images are found.}
        \resumeItem{Automated communication of regressions and updates to developers through email notifications, reducing technical debt and vulnerabilities..}
        \resumeItem{Gained exposure to Docker, Docker Hub, JFrog Artifactory, open-source security tools (Black Duck), and CI/CD processes with Jenkins.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{June 2022 -- May 2024}
      {Merrimack College MackTracker}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented an iOS application sought out by Merrimack College executives to track the on campus shuttle system used by over 5000 students and faculty.}
        \resumeItem{Designed and developed the UI/UX for each screen of the app with familiar user friendly interactions such as by using Google Directions API and Google SSO. }
        \resumeItem{Managed DevOps for development, beta release, and the initial launch.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------HONORS AND AWARDS-----------
\section{Honors and Awards}
\resumeSubHeadingListStart
    \resumeSubheading
      {Very Rev. Mortimer A. Sullivan, O.S.A. Medal}{May 2024}
      {Merrimack College}{}
      \resumeItemListStart
        \resumeItem{Awarded for being the top-ranking Engineering and Computational Sciences student.}
      \resumeItemListEnd

      \resumeSubheading
      {ISG Hackathon Global Finalist}{February 2025}
      {Dell Technologies}{}
      \resumeItemListStart
        \resumeItem{710 projects submitted with 3100 participants.}
      \resumeItemListEnd

      \resumeSubheading
      {Eagle Scout}{November 2020}
      {Boy Scouts of America}{}
    \resumeSubHeadingListEnd

  %-----------Certifications-----------
\section{Certifications}
\resumeSubHeadingListStart
    \resumeSubheading
      {Registered Scrum Master}{January 2025}
      {Agile Education by Scrum Inc}{}
    \resumeSubheading
      {Registered Product Owner}{January 2025}
      {Agile Education by Scrum Inc}{}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Shell, Groovy, Java, Python, Javascript, XSLT, SQL, HTML, CSS, C\#, Dart, R} \\
     \textbf{Technologies}{: Jenkins, Kubernetes, OpenShift, YAML, Linux, REST, Flask, JUnit, Node.js, Express.js, Three.js, Flutter, ASP.NET, .NET, Blazor, Razor, Bootstrap, Docker} \\
     \textbf{Tools}{: GitHub, Jira, Confluence, Scrum, Quay.io, CI/CD, Artifactory, Docker Hub, Figma, Swagger, Postman}
    }}
 \end{itemize}
 
 %-------------------------------------------
\end{document}
